Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-15 papers/integration/omm_integ.tex
Work in progress towards reviewer2's request to enhance the description of the brain model

To the \ccg~model, we added a brainstem model and a biomechanical eye
model. \rvw{The rate-coded brainstem model was taken from the
literature}~\cite{gancarz_neural_1998} as the best-of-breed saccadic
burst generator~\cite{girard_brainstem_2005}.  The biomechanical eye
was implemented using the biomechanical modelling framework OpenSim.
These will be described below, \rvwt{along with a review of
the \ccg~model}, but first we will give a description of the
co-ordinate systems and the modelling framework used.

@@

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model. Fig.~\ref{brain_model} shows the layout of the
populations and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus \citep{robinson_eye_1972}.
% and frontal eye field?

>>>>

To the \ccg~model, we added a brainstem model and a biomechanical eye
model. \rvw{The rate-coded brainstem model was taken from the
literature} \citep{gancarz_neural_1998} as the best-of-breed saccadic
burst generator \citep{girard_brainstem_2005}.  The biomechanical eye
was implemented using the biomechanical modelling framework OpenSim.
These will be described below, \rvwt{along with a review of
the \ccg~model}, but first we will give a description of the
co-ordinate systems and the modelling framework used.

@@

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model, \rvwt{of reflexive saccadic behaviour}.
%
\rvwt{Reflexive saccades are elicited by peripheral changes in the visual
scene and are distinct from voluntary saccades. Reflexive saccades can
occur also as a result of auditory and somatosensory stimuli, but
these modalities are ignored in this work and
in \cite{cope_basal_2017}. The functionality reproduced by
the \ccg~model is `the selection of the best target end-point for a
reflexive saccade'. A competition such as this between competing,
incompatible movements is often referred to as an \e{action selection}
problem. The brain must choose one location to foveate, because the
eyes of most animals can only look in one direction at a time.} % Maybe cite norman_attention_1986, maes_dynamics_1989 on action selection.

\rvwt{It is thought that in vertebrates, the basal ganglia (BG) play an important
r\^ole in action
selection~\citep{redgrave,graybiel,grillner,hikosaka after the
evolutionary paper}. The \ccg~model
places the BG at the centre of the oculomotor system, adopting a
`channel based' model from previous
work~\citep{gurney_basal_2004,etc}. Within the context of the basal
ganglia model, a `channel' is a sub-set of neurons which are
associated with an action. In the oculomotor model, an action
corresponds to a distinct saccade end point. It can be seen that the
action space for reflexive saccade end points is therefore a
continuous space, rather than being selection between distinct
acts. Etc etc. }

Fig.~\ref{brain_model} shows the layout of the populations in the
brain model and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus \citep{robinson_eye_1972}.
% and frontal eye field?
